---
title: "Prep data for NEST"
author: "Audrey Luo"
output: html_document
---

```{r setup, include=FALSE}
library(cowplot)
library(data.table)
library(dplyr)
library(ggplot2)
library(ggpubr)
library(grid)
library(gridExtra)
library(gratia) 
library(kableExtra)
library(mgcv)
library(RColorBrewer)
library(stringr)
library(tidyr)

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE, include = TRUE) 

font_size <- 14
theme_set(theme_classic(base_family = "sans",base_size = font_size))
line_size <- 1
point_size <- 2

input_root <- "/cbica/projects/luo_wm_dev/two_axes_manuscript/input"
output_root <- "/cbica/projects/luo_wm_dev/two_axes_manuscript/output"
```


# Tract Names and Orientations
https://yeatmanlab.github.io/pyAFQ/explanations/bundle_orientation.html#bundle-orientation 
- Left Anterior Thalamic: anterior to posterior
- Right Anterior Thalamic: anterior to posterior
- Left Cingulum Cingulate: anterior to posterior
- Right Cingulum Cingulate: anterior to posterior
- Left Corticospinal: superior to inferior
- Right Corticospinal: superior to inferior
- Left Inferior Fronto-occipital: anterior to posterior
- Right Inferior Fronto-occipital: anterior to posterior
- Left Inferior Longitudinal: anterior to posterior
- Right Inferior Longitudinal: anterior to posterior
- Left Superior Longitudinal: anterior to posterior
- Right Superior Longitudinal: anterior to posterior
- Left Arcuate: anterior to posterior
- Right Arcuate: anterior to posterior
- Left Uncinate: superior to inferior
- Right Uncinate: superior to inferior
- Callosal tracts: right to left
- Left Posterior Arcuate: superior to inferior
- Right Posterior Arcuate: superior to inferior
- Left Vertical Occipital: superior to inferior
- Right Vertical Occipital: superior to inferior

```{r load tract profiles, cache=TRUE}
HBN <- readRDS(sprintf("%1$s/%2$s/derivatives/tract_profiles_ACT/all_subjects/ACT_noUF/collated_tract_profiles_final_ACT_noUF.RData", input_root, "HBN"))


# format tract profiles df's
format_tract_profiles <- function(df) {
  
  # make tract_label
  df <- df %>% mutate(tract_label = gsub("_", " ", tractID) %>%
                       gsub("Left|Right", "", .) %>%
                       gsub("Fronto.occipital", "Fronto-occipital", .) %>% # change to hyphen for plotting purposes
                       trimws())
  
  # label main orientation
  df <- df %>% 
  mutate(main_orientation = case_when(
    tract_label %in% c("Anterior Thalamic", "Cingulum Cingulate", "Inferior Fronto-occipital",
                   "Inferior Longitudinal", "Superior Longitudinal") ~ "AP",
    tract_label %in% c("Arcuate", "Uncinate") ~ "AP_frontal_temporal",
    tract_label %in% c("Callosum Anterior Frontal", "Callosum Motor", "Callosum Occipital", "Callosum Orbital", 
                       "Callosum Posterior Parietal", "Callosum Superior Frontal", "Callosum Superior Parietal", "Callosum Temporal") ~ "RL",
    tract_label %in% c("Corticospinal", "Posterior Arcuate","Vertical Occipital") ~ "SI",
    TRUE ~ NA_character_
  ))

  df$main_orientation <- as.factor(df$main_orientation)
  return(df)
}


 HBN_tp <- format_tract_profiles(HBN)
    
saveRDS(HBN_tp, sprintf("%1$s/%2$s/tract_profiles/tract_profiles_for_NEST_withACT.RData", output_root, "HBN"))
```

