---
title: "HCPD Final Sample Selection"
author: "Audrey Luo"
output:
  html_document:
    code_folding: show
    highlight: haddock
    theme: lumen
    toc: yes
    toc_depth: 4
    toc_float: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(data.table)
library(dplyr)
library(purrr)
library(rjson)
library(stringr)
library(tidyr)
```


## Load initial sample list
```{r}
sub_id <- read.table("/cbica/projects/luo_wm_dev/two_axes_manuscript/input/HCPD/subject_list/HCPD_subject_list_babs.txt", header = T)
demographics.temp <- read.csv("/cbica/projects/luo_wm_dev/two_axes_manuscript/input/HCPD/sample_selection_files/HCPD_WMDev_TempSampleDemographics_N572_age8to22.csv")
dwi.qc.temp <- read.csv("/cbica/projects/luo_wm_dev/two_axes_manuscript/input/HCPD/sample_selection_files/HCPD_WMDev_TempSampleQCMetrics_N572_age8to22.csv")
```

## Incomplete Data Processing Exclusion
```{r}
# 3 subjects failed qsirecon
fail_qsirecon <- read.table("/cbica/projects/luo_wm_dev/input/HCPD/sample_selection_files/failed_qsirecon.txt", sep = ",")
sub_id <- sub_id[!sub_id$sub_id %in% fail_qsirecon$V1,] %>% as.data.frame() %>% setNames("sub_id") #remove 3 participants from the sample of 572 due to failure to complete qsirecon, final N = 569
# technically, these subjects are already excluded in collated_tract_profiles_nocovbat_tmp.tsv below. But just wanted to look at who failed babs

# no subjects are missing freesurfer
```

After running ACT + pyAFQ, many subjects are missing one or more tracts. We can't harmonize a subject's data if they are missing ANY tracts. To keep exclusion criteria consistent across datasets, we are excluding people who are missing bundles that we need for this study.

Note that there are some bundles that are OKAY if they are missing because we are excluding some from analyses:
- cingulum cingulate
- anterior thalamic radiation
```{r}
# load the tract profiles of subjects who are missing at least 1 tract
missing_tracts <- fread("/cbica/projects/luo_wm_dev/input/HCPD/derivatives/tract_profiles/all_subjects/missing_tract_profiles_nocovbat.tsv")
# load full tract profiles of everyone (except for the subjects in missing_tracts)
HCPD_all <- fread("/cbica/projects/luo_wm_dev/input/HCPD/derivatives/tract_profiles/all_subjects/collated_tract_profiles_nocovbat_tmp.tsv") # takes a while to load
required_tracts <- unique(HCPD_all$tractID)

##########################
# missing tract exclusion
##########################
# it's okay if a participant is missing these tracts
allowed_missing_tracts <- c("Cingulate", "Anterior Thalamic")

# summarize tracts present for each subject
tract_summary <- missing_tracts %>%
  distinct(sub, tractID) %>%
  group_by(sub) %>%
  summarize(tracts_present = list(tractID), .groups = "drop")

# identify missing tracts for each subject
subjects_missing_tracts <- tract_summary %>%
  mutate(missing_tracts = map(tracts_present, ~ setdiff(required_tracts, .x))) %>%
  select(sub, missing_tracts)
 
# have one row per missing tract
missing_tracts_long <- subjects_missing_tracts %>%
  unnest(cols = c(missing_tracts))

missing_tracts_count <- missing_tracts_long %>%
  group_by(missing_tracts) %>%  # Group by missing tracts
  summarise(count = n()) 

# identify subjects to exclude
# A subject should be excluded if they are missing any REQUIRED tracts (aka tracts not in "allowed_missing_tracts")
# determine the subjects are missing needed tracts  
unacceptable_missing_tracts <- missing_tracts_long %>%
  filter(!str_detect(missing_tracts, paste(allowed_missing_tracts, collapse = "|")))

# get unique subjects who have any unacceptable missing tracts
subjects_to_exclude <- unacceptable_missing_tracts %>%
  distinct(sub)

# count the number of excluded subjects
num_excluded_subjects <- nrow(subjects_to_exclude)
cat("Number of subjects excluded:", num_excluded_subjects, "\n")

write.table(subjects_to_exclude, "/cbica/projects/luo_wm_dev/two_axes_manuscript/input/HCPD/sample_selection_files/subs_missing_tracts.txt", col.names=T, row.names=F, quote = TRUE)

sub_id <- sub_id[!sub_id$sub_id %in% subjects_to_exclude$sub,] %>% as.data.frame() %>% setNames("sub_id") # remove 1 participant from sample of 569 due to failing qsiprep/qsirecon, new N = 568
```

```{r}
# add back subjects that are missing non-important tracts. save HCPD tract profiles
# Identify subjects missing only non-essential tracts (tracts in allowed_missing_tracts)
# = identify subjects who are not in the exclusion list
subjects_with_allowed_missing_tracts <- missing_tracts_long %>%
  filter(sub %notin% subjects_to_exclude$sub) %>%
  filter(str_detect(missing_tracts, paste(allowed_missing_tracts, collapse = "|")))

# get sub ids
subjects_with_allowed_missing_tracts <- subjects_with_allowed_missing_tracts %>%
  distinct(sub)

# add these subjects' data back to the full tract profiles data (should be 0 participants added back)
HCPD_all_with_allowed <- bind_rows(HCPD_all, missing_tracts %>% filter(sub %in% subjects_with_allowed_missing_tracts$sub))
HCPD_all_with_allowed <- HCPD_all_with_allowed %>%
  distinct()

# remove the tracts we don't need
HCPD_all_with_allowed <- HCPD_all_with_allowed %>% filter(!str_detect(tractID, paste(allowed_missing_tracts, collapse = "|")))

write.table(HCPD_all_with_allowed, "/cbica/projects/luo_wm_dev/two_axes_manuscript/input/HCPD/derivatives/tract_profiles/all_subjects/collated_tract_profiles_nocovbat.tsv", row.names = FALSE)
```

## Save Final Sample: Subject List, Demographics, QC measures
```{r}
# Make final sample demographics dataframe
demographics.final <- demographics.temp[demographics.temp$sub %in% sub_id$sub_id,] %>% select(sub, age, sex, race, site) # combine demographics data 
 
# Make final sample QC metrics dataframe 
dwi.qc.final <- dwi.qc.temp[dwi.qc.temp$sub %in% sub_id$sub_id,] %>% select(sub, mean_fd, t1_neighbor_corr) 

write.table(sub_id, "/cbica/projects/luo_wm_dev/two_axes_manuscript/input/HCPD/subject_list/final_sample/HCPD_WMDev_FinalSample.txt", col.names=T, row.names=F, quote = TRUE)
write.csv(merge(demographics.final, dwi.qc.final), "/cbica/projects/luo_wm_dev/two_axes_manuscript/input/HCPD/sample_selection_files/final_sample/HCPD_WMDev_FinalSampleDemoQC.csv", quote = F, row.names = F)
```

## Demographics table
```{r}
final_sample <- read.csv("/cbica/projects/luo_wm_dev/two_axes_manuscript/input/HCPD/sample_selection_files/final_sample/HCPD_WMDev_FinalSampleDemoQC.csv", header=T)

# demographic variables to summarize
demo_vars <- c("sex", "race")

# function to summarize the demographic variables
summary_list <- map(demo_vars, function(var) {
  final_sample %>%
    group_by(.data[[var]]) %>%
    summarise(count = n(),
              percent = (n() / nrow(final_sample)) * 100)})

# summaries for each variable
summary_list

range(final_sample$age)
mean(final_sample$age)
sd(final_sample$age)
```

